CPU-Scheduling

### 2024-10-18 Handout/article.tex
added SJF to .tex

# Adding a new process
def add_client(name):
  list.append(name)

@@

As you can see the implementation is itself pretty easy.

@@

@@

>>>>

# Adding a new process
def add_client(client):
  list.append(client)

@@

As you can see the implementation is itself pretty easy.
\pagebreak

@@

Now the situation changes a bit. 
The infamous family of five wants to go first, however the cashier picks you first after seeing, that you only have a few items.
This is the "Shortest Job First" (SJF).

\begin{lstlisting}[language=Python, style=colorEX]
# Simple implementation of SJF in Python

# Define client class and list
class Client:
  def __init__(self, ttc): # ttc as time to completion
    self.ttc = ttc
    # other stuff that is relevant for the client class

list = []

# Adding a new process
client = Client(ttc) 
def add_client(client): 
  list.append(client)

# Decide which process is next
def allocate():
  list.sort(key=lambda a: a.ttc) # sort according to ttc
  next = list.pop(0)
  use_resource(next) # function that will allow "next" to use the CPU
\end{lstlisting}

There are two notable changes in this code snippet, when compared to FIFO. One of them is relevant.
First, the less exiting part is that I actually took my time to write out some of the client class definition.
Second and the real difference to FIFO is that we sort the according to the time to completion. 
This means that we will choose the task with the shortest time to completion.
AT THIS PART THE KNOWLEDGE OF PROPER SORTING ALGORITHMS IS MISSING: MAYBE A REVERSE BUBBLE SORT? 
THE LIST SHOULD BE ALREADY SOMEWHAT ORDERED AND THE LAST MEMBER HAS TO BE SORTED
The only problem is when you arrive late. The scanning of products already started and you'll have to wait.
This policy is a so called non-preemptive policy.
"Non-preemptive" just means that once a task will run until it finishes.

@@

TODOS:
- PROPERLY LABEL IMAGES AND CODE BLOCKS
